---
---
Bible Word Cloud
=============================
###Rowen Remis R. Iral
####2014 September 07

Data Scientist with MBA, IT Engineer certification, Marketing Mastery(Internet Marketer) and Solutions Architect (Cloud)

http://wenup.wordpress.com
http://wenmi01.tublr.com

--
The goal of this data is to show the word cloud from the King James Version of the Bible.

##System that Run this knitted Document
Ubuntu 64-bit running on a Koding.com server (free)
  with RStudio Server

--
##Getting the Data
Our data can be downloaded from:
```
http://printkjv.ifbweb.com/AV_txt.zip
```

##Downloading the Zip File
```{r}
download.file(url = "http://printkjv.ifbweb.com/AV_txt.zip", destfile="AV_txt.zip", method="curl")
```

##Unzip the KJV Bible
```{r}
unzip("AV_txt.zip")
```

##Bible Variable
```{r}
bible <- readLines(con <- file("AV1611Bible.txt"))
```

##Processing the Bible
In order to create the word cloud, we will need the tm and wordcloud packages in R.
These are text mining and world cloud plotting tools.
```{r}
library(tm)
library(wordcloud)
corp <- Corpus(VectorSource(bible))
corp <- tm_map(corp,removePunctuation)
corp <- tm_map(corp, function(x)removeWords(x,stopwords()))
```

##Create the Wordcloud
```{r}
#png("bible_word_cloud_rri.png", width=1280,height=800)
pal2 <- brewer.pal(8,"Dark2")
wordcloud(corp, random.order=FALSE, colors=pal2, rot.per=.15)
#dev.off()
```
The word cloud of Bible